О множествах точек на плоскости с целочисленными расстояниями

### 2019-06-09 pps-linear-bound/pps-linear-lower-bound.tex
Fix language issue

We can improve the constant in Theorem~\ref{thm:main_estimate} if new exact values of $d(2,n)$ are found;
however, the obtained constant is bounded by $3^{1/4}\cdot2^{-3/2}$.
To be precise, we have the following

>>>>

We can improve the constant in Theorem~\ref{thm:main_estimate},
if some new exact values of $d(2,n)$ are found;
however, the obtained constant is bounded by $3^{1/4}\cdot2^{-3/2}$.
To be precise, we have the following
